Music Perception: Pilot Accuracy Analysis

### 2021-01-25 analysis/analysis.Rmd
correct outlines
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## 2. Teaching stimuli
### All
```{r item1, echo = FALSE}
# individual
ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data2 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]

@@

### articulation
```{r item1-a, echo = FALSE}
subset2_a <- subset2[Skill == "articulation"]
subset2_a$MidFile <- gsub("a_t_", "", subset2_a$MidFile)
subset2_a[order(-Mean_Percent)]

@@

### dynamics
```{r item1-d, echo = FALSE}
subset2_d <- subset2[Skill == "dynamics"]
subset2_d$MidFile <- gsub("d_t_", "", subset2_d$MidFile)
subset2_d[order(-Mean_Percent)]

@@

## 3. performing (each item)
### all
```{r item2, echo = FALSE}
# individual
ind_data3 <- data[subjectNumber != 9 & Condition == "performing", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data3 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]

@@

### articulation
```{r item2-a, echo = FALSE}
subset3_a <- subset3[Skill == "articulation"]
subset3_a$MidFile <- gsub("a_p_", "", subset3_a$MidFile)
subset3_a[order(-Mean_Percent)]

@@

### dynamics
```{r item2-d, echo = FALSE}
subset3_d <- subset3[Skill == "dynamics"]
subset3_d$MidFile <- gsub("d_p_", "", subset3_d$MidFile)
subset3_d[order(-Mean_Percent)]

>>>>

## 2. Teaching stimuli
### All
```{r item1, echo = FALSE}
# individual
ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data2 <- ind_data2[order(subjectNumber, Condition, Skill, MidFile)]

@@

### Articulation
```{r item1-a, echo = FALSE}
subset2_a <- subset2[Skill == "articulation"]
subset2_a$MidFile <- gsub("a_t_", "", subset2_a$MidFile)
subset2_a[order(-Mean_Percent)]

@@

### Dynamics
```{r item1-d, echo = FALSE}
subset2_d <- subset2[Skill == "dynamics"]
subset2_d$MidFile <- gsub("d_t_", "", subset2_d$MidFile)
subset2_d[order(-Mean_Percent)]

@@

## 3. Performing stimuli
### All
```{r item2, echo = FALSE}
# individual
ind_data3 <- data[subjectNumber != 9 & Condition == "performing", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data3 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]

@@

### Articulation
```{r item2-a, echo = FALSE}
subset3_a <- subset3[Skill == "articulation"]
subset3_a$MidFile <- gsub("a_p_", "", subset3_a$MidFile)
subset3_a[order(-Mean_Percent)]

@@

### Dynamics
```{r item2-d, echo = FALSE}
subset3_d <- subset3[Skill == "dynamics"]
subset3_d$MidFile <- gsub("d_p_", "", subset3_d$MidFile)
subset3_d[order(-Mean_Percent)]
